\textbf{ADC} - Analog to Digital Converter.

\textbf{ASIC} - Application Specific Integrated Circuit.

\textbf{COTS} - Commercial Off-The-Shelf.

\textbf{dB} - Decibel.

\textbf{dBm} - Decibel power ratio with reference to 1 mW.

\textbf{DDS} - Direct Digital Synthesis. 

\textbf{DSP} - Digital Signal Processing.

\textbf{DUT} - Device Under Test. With reference to a VNA, the device connected to VNA's ports being measured. 

\textbf{FPGA} - Field Programmable Gate Array.

\textbf{ISM} - Industrial Scientific Medical.

\textbf{IP3} - Third Order Intermodulation Product.

\textbf{I/Q} - In-phase / Quadrature. Used in DSP to represent two sinusoids which are 90 degrees out of phase. 

\textbf{LO} - Local Oscillator. 

\textbf{P1dB} - 1 dB Compression Point. 

\textbf{PA} - Power Amplifier.

\textbf{PCB} - Printed Circuit Board. 

\textbf{PCBA} - Printed Circuit Board Assembly.

\textbf{PLL} - Phase Locked Loop.

\textbf{RF} - Radio Frequency.

\textbf{RFIC} - Radio Frequency Integrated Circuit

\textbf{S-parameters} - Scattering Parameters. Elements of a scattering matrix which describe the behaviour of linear electrical networks. 

\textbf{S\textsubscript{MN}} - S-paramater describing the relationship between ports M and N in an electrical system. Common s-parameters are S\textsubscript{11} which represents the reflected power incident on port one, and S\textsubscript{21}, which represents the gain of a DUT between ports 2 and 1. 

\textbf{SMT} - Surface Mount Technology.

\textbf{SPDT} - Single Pole Double Throw switch. 

\textbf{SP4T} - Single Pole 4 Throw switch. 

\textbf{VCO} - Voltage Controlled Oscillator.

\textbf{VNA} - Vector Network Analyser. Electronic test and measurement instrument which measures s-parameters of electrical networks. 

\textbf{VSWR} - Voltage Standing Wave Ratio
